---
title             : "Working with Papaja"
shorttitle        : "Lab 8"

author: 
  - name          : "Anwesha Guha"
    affiliation   : "1"

  - name          : "Heidi Iwashita"
    affiliation   : "1"

  - name          : "Christopher Loan"
    affiliation   : "1"

  - name          : "Adam Nielsen"
    affiliation   : "1"

  - name          : "Aaron Rothbart"
    affiliation   : "1"

            
affiliation:
  - id            : "1"
    institution   : "University of Oregon"

authornote: |
  For the purpose of EDLD 651 to work with Papaja.

abstract: |
  This paper will explore the process of learning papaja with our super awesome group.
  
keywords          : "papaja, lab"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(janitor)
library(rio)
library(knitr)
library(here)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r global options, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.height = 8,
                      fig.width = 6.5,
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE)
```

```{r data}
star <- import(here("data", "star.csv"))
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

@iwashita2019 reported results of a study investigating validity, reliability and clinical feasibility of pragmatic rating scales for assessing social communication after brain injury. 

This paper reports on a secondary analysis of data from recovery high schools [@tanner2020].

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
