---
title             : "Working with Papaja"
shorttitle        : "Lab 8"

author: 
  - name          : "Anwesha Guha"
    affiliation   : "1"

  - name          : "Heidi Iwashita"
    affiliation   : "1"

  - name          : "Christopher Loan"
    affiliation   : "1"

  - name          : "Adam Nielsen"
    affiliation   : "1"

  - name          : "Aaron Rothbart"
    affiliation   : "1"

            
affiliation:
  - id            : "1"
    institution   : "University of Oregon"

authornote: |
  For the purpose of EDLD 651 to work with Papaja.

abstract: |
  This paper will explore the process of learning papaja with our super awesome group.
  
keywords          : "papaja, lab"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(janitor)
library(rio)
library(knitr)
library(here)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r global options, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.height = 8,
                      fig.width = 6.5,
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE)
```

```{r data}
star <- import(here("data", "star.csv"))

star_summary<-star %>%
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss),
            math_sd = sd(tmathss),
            rdg_mean = mean(treadss),
            rdg_sd = sd(treadss))

star_summary %>% 
  kable(digits = 2)

```

This table displays the means and standard deviations of both math and reading scores, group by sex and frl.

```{r}
star %>% 
  ggplot(aes(x = totexp, y = tmathss)) + 
  geom_point(color = 'gray70') + 
  geom_smooth(aes(group = frl, color = frl), method = 'lm') + 
  labs(x = 'Teacher Experience (years)', 
       y = 'Total Math Scale Score', 
       title = 'Relation between teacher experience and math scores',
       subtitle = 'Separate regression lines displayed by free/reduced price lunch status', 
       color = 'Lunch status'
       ) +
  theme_minimal() + 
  scale_color_discrete(labels = c('Paid Meals','Free/Reduced Price Meals'))+
  theme(legend.position = 'bottom')
```

Above is a figure that shows two regression lines for the relationship between teacher experience and total math scale score. The above line represents those who do not qualify for free/reduced price lunch, whereas the bottom represents those who do qualify.

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

@iwashita2019 reported results of a study investigating validity, reliability and clinical feasibility of pragmatic rating scales for assessing social communication after brain injury. 

This paper reports on a secondary analysis of data from recovery high schools [@tanner2020].

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
